\chapter{Preface}
I did start my journey to become a shipbuilder in 2011. Delft has become my second home in the years since. In those years I have not only been introduced in the world of shipbuilding. But I have also developed myself towards a "Delftse Ingenieur". This report is the last step in this journey. And although the writing of this report has been an individual accomplishment. I could not have done it without the help of some very talented, critical, caring and enthusiastic people around me.

First of all, I would like to thank all the people I have met at Damen Shipyards, where the doors were always open to ask questions and discuss our extraordinary industry. A special thanks to Toine Cleophas, my supervisor at Damen. Besides being a supervisor, he has also been my mentor. He showed me the maritime industry and Damen from his perspective, which I could not have learned at any university. Thank you for the late afternoon discussions at the office, in the car, and with a beer in our hand.

Furthermore, I would like to thank Robert Hekkenberg as a guide in the world of academics. By questioning the steps I took and guiding the scope. He has helped me through many iterations, which have resulted in not only a good design, but also a design well sold.

Another thank you goes to Mark Neerincx, as supervisor, he has helped me to explore the world of human-computer interaction research. With his academic knowledge and practical experience did he help me to keep the balance between developing knowledge and a product.

Beside my supervisors have there been many more people involved in the steps taken, which resulted in this thesis. It is not possible to name all of you.
I want and need to show my utmost gratitude to some exceptional people. My parents, pappa and mamma, I want to thank you for giving me the roots to get back to, and wings to fly beyond the horizon.\\


\begin{flushright}
	\textit{Ingmar Wever\\
		Amsterdam, December 2018}
\end{flushright}