\chapter{Basic design}
To test the different scenarios a tool will be build. This tool will be able to simulate the scenarios to get more insight why decisions are made. Full scale testing will cost much more time and effort as it is harder to control. 
The development will be based on the principles from the Agile Manifesto, as this has proven to result in effective software. This means there will be a start with a basic tool, which will continuously be improved. Changes in requirements might appear trough out the whole process, to deliver a better tool. Thereby must be kept in mind that working software is the primary measure of progress. This is only possible when the software is sustainable and thus easy to maintain and improve, which is only possible with a good design. Keeping it simple will be key in this process. Thereby reflective moments are needed to check if the chosen path is the right one, or if the direction should be adapted.

\section{Requirements}
The first step is to set the goals or requirements of the software. This doesn't mean it is a full description of the software, but features it should at least have to be able to answer the research questions.
The most important requirement is that ships within the simulation behave similarly to ships in reality. This does not necessarily mean that all hydromechanics should be known. But ships should have similar ways of turning and changing speed. This can be based on sea-trials and done using a mapping from current speed, current rotation, rudder angle and throttle to future speed and turning speed.
The second requirement should be that it is flexible, in a way that different scenarios can be added and tested easily. Thereby changing ship characteristics, shared information and other inputs.
Thirdly, it must be possible to show the register of possible decisions for the different vessels. To be able to validate this with seafarers. Meaning it will be a white box model.

\section{User stories}
The next step is to define users stories from the requirements. User stories are in a form: \emph{"As a [user] I want [action] so that [result]"}. Extending them with an acceptance criteria this will result in the features which should be implemented.

Within this application there will be different roles. For which these user stories can be used. Below these are described:
\begin{itemize}
	\item \emph{Operator}. The person who set-up the simulation and fills in the different properties for the ships and specific scenario.
	\item \emph{Viewer}. Someone who uses the application to view a specific scenario. Thereby trying to answer the research questions.
	\item \emph{Ship}. Object in the map which is used by the simulation. But to work correctly it also had needs for information.
\end{itemize}

Some examples of those user stories are given below. All users stories can be found in appendix XXX.\todo{add user stories to appendix}. 

\begin{itemize}
	\item As an operator, I want to add vessels to the map, by selecting them in a list, so that they become part of the simulation. \\
	Acceptance criteria: Ship visualized and other ships start receiving information.
	\item As a viewer, I want to to be able to get the belief state, intention and next action of a ship, so that I can verify if it is what I expected it to be. \\
	Acceptance criteria: Belief state, intention and next action are shown.
	\item As a ship, I want to be able to predict the path of other vessels, so that I can make my decisions based on this. \\
	Acceptance criteria: correctly updated belief state about other vessels.
\end{itemize}

\section{User interactions}
What should de different modules do

\section{Assumptions}
Questions, clarifications and scope